Quality Definitions of Qualities

### 2019-11-21 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
updated all of my qualities PM

\subsection{\notdone{Robustness} \pmi{owner}}
\begin{defn}
  The degree to which a system or component can function correctly in the
  presence of invalid inputs or stressful environmental conditions
  \citep{IEEEStdGlossarySET1990}.
\end{defn}
\begin{defn}
  The quality can be further informally refined as the ability of a software to
  keep an acceptable behaviour, expressed in terms of robustness requirements, in
  spite of exceptional or unforeseen execution conditions (such as the
  unavailability of system resources, communication failures, invalid or
  stressful inputs, etc.) \citep{fernandez2005model}.
\end{defn}
\begin{defn} \label{RobustnessPartialDefn}
  Code possesses the characteristic of robustness to the extent that it can
  continue to perform despite some violation of the assumptions in its
  specification \citep{boehm2007software}.
\end{defn}
\begin{defn} \label{RobustnessDefnSelected}
  A program is robust if it behaves ``reasonably'', even in circumstances that
  were not anticipated in the requirements specification - for example, when it
  encounters incorrect input data or some hardware malfunction
  \citep{ghezzi1991fundamentals}.
\end{defn}

@@

Definition \ref{RobustnessDefnSelected} rephrased \wss{Aren't you really
  combining Definition~\ref{RobustnessDefnSelected} with
  Definition~\ref{RobustnessPartialDefn}?} : Software possesses the
characteristic of robustness if it behaves ``reasonably'' in two situations: i)
when it encounters circumstances not anticipated in the requirements
specification; and ii) when the assumptions in its requirements specification
are violated.

@@

\pmi{Still want to refine what we mean by reasonable}

@@

This definition includes all important categories of performance.  \wss{What are
  the important categories?}

@@

\begin{defn} \label{MaintainabilityDefnSelected1}
The ease with which a software system or component can be modified to correct
faults, improve performance or other attributes, or adapt to a changed
environment \citep{IEEEStdGlossarySET1990}. 
\end{defn}
\begin{defn}
ISO/IEC 25010 refers to maintainability as the degree of effectiveness and
efficiency with which a product or system can be modified by the intended
maintainers \citep{ISO/IEC25010}. \wss{The author needs to be updated so that
  this display properly.}
\end{defn}
\begin{defn}
Effort required to locate and fix an error in a program
\citep{pressman2005software}.
\end{defn}
\begin{defn}
A set of attributes that bear on the effort needed to make specified
modifications (which may include corrections, improvements, or adaptations of
software to environmental changes and changes in the requirements and functional
specifications) \citep{pfleeger2006software}.
\end{defn}
\begin{defn}
We will view maintainability as two separate qualities: repairability and
evolvability. Software is repairable if it allows the fixing of defects; it is
evolvable if it allows changes that enable it to satisfy new requirements
\citep{ghezzi1991fundamentals}.
\end{defn}
\begin{defn} \label{MaintainabilityDefnSelected2}
Code possesses the characteristic of maintainability to the extent that it
facilitates updating to satisfy new requirements or to correct deficiencies
\citep{boehm2007software}.
\end{defn}

\begin{defn}
  The effort required to locate and fix an error in an operational program
  \citep{McCallEtAl1977}. (As summarized in \citet{VanVliet2000}.) \wss{It looks
    like \citet{pressman2005software} was using \citet{McCallEtAl1977} for their
    definition.} \wss{PM - can you please look into whether
    \citet{pressman2005software} cite \citet{McCallEtAl1977}?  Do they give a
    reason for dropping the word operational?}
\end{defn}

@@

This definition includes all potential reasons to modify the software.
\wss{What are the potential reasons?  How do you know that we haven't missed
  any?}  \wss{What are the other attributes?  What is an attribute?  Is it the
  same as a quality?  We are calling performance a quality in this document.}

\subsection{\notdone{Reusability} \pmi{owner}}

@@

\pmi{I think this is done.} \wss{Looks good at this time.}

@@

Definition \ref{PortabilityDefnSelected} rephrased: Effort required to transfer
a program between system environments. \wss{Should we clarify what a system
  environment is?  What is a system environment?  Hardware and OS?}

>>>>

\subsection{{Robustness} \pmi{owner}}
\begin{defn}
  The degree to which a system or component can function correctly in the
  presence of invalid inputs or stressful environmental conditions
  \citep{IEEEStdGlossarySET1990}.
\end{defn}
\begin{defn}
  The quality can be further informally refined as the ability of a software to
  keep an acceptable behaviour, expressed in terms of robustness requirements, in
  spite of exceptional or unforeseen execution conditions (such as the
  unavailability of system resources, communication failures, invalid or
  stressful inputs, etc.) \citep{fernandez2005model}.
\end{defn}
\begin{defn} \label{RobustnessPartialDefn}
  Code possesses the characteristic of robustness to the extent that it can
  continue to perform despite some violation of the assumptions in its
  specification \citep{boehm2007software}.
\end{defn}
\begin{defn} \label{RobustnessDefnSelected}
  A program is robust if it behaves ``reasonably'', even in circumstances that
  were not anticipated in the requirements specification - for example, when it
  encounters incorrect input data or some hardware malfunction
  \citep{ghezzi1991fundamentals}.
\end{defn}

@@

Definition \ref{RobustnessPartialDefn} and Definition \ref{RobustnessDefnSelected} rephrased: Software possesses the
characteristic of robustness if it behaves ``reasonably'' in two situations: i)
when it encounters circumstances not anticipated in the requirements
specification; and ii) when the assumptions in its requirements specification
are violated.

@@

\pmi{Still may want to refine what we mean by reasonable}

@@

This definition offers a comprehensive list of constraints that are commonly associated with software performance, such as speed, throughput, capacity, and timing.

\pmi{I will check if Wiegers discusses the difference between speed and timing.}

@@

\begin{defn} \label{MaintainabilityDefnSelected1}
The ease with which a software system or component can be modified to correct
faults, improve performance or other attributes, or adapt to a changed
environment \citep{IEEEStdGlossarySET1990}. 
\end{defn}
\begin{defn}
ISO/IEC 25010 refers to maintainability as the degree of effectiveness and
efficiency with which a product or system can be modified by the intended
maintainers \citep{ISO/IEC25010}.
\end{defn}
\begin{defn}
Effort required to locate and fix an error in a program
\citep{pressman2005software}.
\end{defn}
\begin{defn}
A set of attributes that bear on the effort needed to make specified
modifications (which may include corrections, improvements, or adaptations of
software to environmental changes and changes in the requirements and functional
specifications) \citep{pfleeger2006software}.
\end{defn}
\begin{defn}
We will view maintainability as two separate qualities: repairability and
evolvability. Software is repairable if it allows the fixing of defects; it is
evolvable if it allows changes that enable it to satisfy new requirements
\citep{ghezzi1991fundamentals}.
\end{defn}
\begin{defn} \label{MaintainabilityDefnSelected2}
Code possesses the characteristic of maintainability to the extent that it
facilitates updating to satisfy new requirements or to correct deficiencies
\citep{boehm2007software}.
\end{defn}

\begin{defn}
  The effort required to locate and fix an error in an operational program
  \citep{McCallEtAl1977}. (As summarized in \citet{VanVliet2000}.) \wss{It looks
    like \citet{pressman2005software} was using \citet{McCallEtAl1977} for their
    definition.} \wss{PM - can you please look into whether
    \citet{pressman2005software} cite \citet{McCallEtAl1977}?  Do they give a
    reason for dropping the word operational?}
\pmi{Yes, \citet{pressman2005software} does cite the relevant section of the textbook with \citet{McCallEtAl1977}. While they do not give a reason for specifically dropping the word operational, they do indicate that their given definition ``is a very limited definition''. Perhaps their intent was breadth.}
\end{defn}

@@

This definition offers a comprehensive list of potential reasons for modifying software, such as correcting faults, improving performance or other attributes, or satisfying new requirements.

 \wss{What are the other attributes?  What is an attribute?  Is it the
  same as a quality?  We are calling performance a quality in this document.}
\pmi{The term quality attribute has come up often in the literature - qualities appear to be a subset of attributes. Quality attributes seem to be associated with non-functional requirements. The term resource attribute was encountered in a journal and implied an association with a functional requirement. The two might differ along those lines of NFR and FR.}

\pmi{I think this is done}

\subsection{{Reusability} \pmi{owner}}

@@

@@

Definition \ref{PortabilityDefnSelected} rephrased: Effort required to transfer
a program between system environments (including hardware and software).
